Machine Learning Manuscript Outline

### 2018-11-14 results/tables/Table1.Rmd
fix commented code

####################################################################################################
#------------------------------- Read in necessary libraries --------------------------------------#
####################################################################################################deps = c("knitr","rmarkdown","vegan","gtools", "tidyverse");
for (dep in deps){
  if (dep %in% installed.packages()[,"Package"] == FALSE){
    install.packages(as.character(dep), quiet=TRUE);
  }
  library(dep, verbose=FALSE, character.only=TRUE)
}

#####################################################################################################------------------------------- Define knitr options to allow kable ------------------------------#
####################################################################################################options(kableExtra.latex.load_packages = FALSE)
options(kableExtra.auto_format = FALSE)
options(knitr.table.format = "latex")
library(kableExtra)
```

@@

##################################################################################################### We load a model parameters file to make our Table 1. Model parameters file has the information of optimized hyper-parameters, pre-processing and cross-validation methods and software implementation for all the classification algorithms.

>>>>

####################################################################################################
#------------------------------- Read in necessary libraries --------------------------------------#
####################################################################################################
deps = c("knitr","rmarkdown","vegan","gtools", "tidyverse");
for (dep in deps){
  if (dep %in% installed.packages()[,"Package"] == FALSE){
    install.packages(as.character(dep), quiet=TRUE);
  }
  library(dep, verbose=FALSE, character.only=TRUE)
}

#####################################################################################################
#------------------------------- Define knitr options to allow kable ------------------------------#
####################################################################################################
options(kableExtra.latex.load_packages = FALSE)
options(kableExtra.auto_format = FALSE)
options(knitr.table.format = "latex")
library(kableExtra)
```

@@

#####################################################################################################

# We load a model parameters file to make our Table 1. Model parameters file has the information of optimized hyper-parameters, pre-processing and cross-validation methods and software implementation for all the classification algorithms.
